### 2015-01-11 paper/Content/sources.tex
Aligned sources

\bibitem{SDKFragments}
Google Inc., \emph{Android Developers -- Fragments},
[Online]. http://developer.android.com/guide/components/fragments.html(retrieved 05-Jan-2015)

@@

\bibitem{FowlerMvpRetirementNote}
Fowler, Martin: \emph{Retirement note for Model View Presenter Pattern},
[Online]. http://martinfowler.com/eaaDev/ModelViewPresenter.html (retrieved 10-Jan-2015)

@@

\bibitem{FowlerSupervisingController}
Fowler, Martin: \emph{Supervising Controller},
[Online]. http://martinfowler.com/eaaDev/SupervisingPresenter.html (retrieved 10-Jan-2015)

\bibitem{FowlerPassiveView}
Fowler, Martin: \emph{Passive View},
[Online]. http://martinfowler.com/eaaDev/PassiveScreen.html (retrieved 10-Jan-2015)

%\bibitem{}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

\bibitem{SDKFragments}
Google Inc., \emph{Android Developers -- Fragments},
[Online]. http://developer.android.com/guide/components/fragments.html (retrieved 05-Jan-2015)

@@

\bibitem{FowlerMvpRetirementNote}
M. Fowler: \emph{Retirement note for Model View Presenter Pattern}, 2006, 
[Online]. http://martinfowler.com/eaaDev/ModelViewPresenter.html (retrieved 10-Jan-2015)

@@

\bibitem{FowlerSupervisingController}
M. Fowler: \emph{Supervising Controller}, 2006, 
[Online]. http://martinfowler.com/eaaDev/SupervisingPresenter.html (retrieved 10-Jan-2015)

\bibitem{FowlerPassiveView}
M. Fowler: \emph{Passive View}, 2006, 
[Online]. http://martinfowler.com/eaaDev/PassiveScreen.html (retrieved 10-Jan-2015)
